\section{Implementation Details}


\subsection{Procrustes Solver Details}

Our pose solver is the one introduced in FlowCam \cite{smith2023flowcam}; see \cite{smith2023flowcam} for details. 
The only difference is that instead of selecting 1000 random points for the Procrustes estimation, we fix the points (uniformly spaced throughout the image) when performing per-scene overfitting.
We find that fixing the points used for the pose solver allows the network to better overfit confidence weights and subsequently yields better poses.

\subsection{Intrinsics Solver Details}
For the intrinsics solver, we assume a pinhole camera estimate and discretize a set of 60 candidate focal lengths between .5 and 2 (in resolution-independent units).
We use a softmin on the flow error maps, as discussed in the main paper.
We scale the error maps by a temperature factor of 10 and weight the error maps by the flow confidence weights.
See \cref{fig:focal_and_depth} for illustration.

\subsection{Depth NN (MiDaS) details}
For our depth network, we use the lightweight CNN version of MiDaS \cite{ranftl2020towards}, pretrained with the publicly available weights trained on relative-depth estimation.

\subsection{Correspondence Weight MLP}
The correspondence weight MLP is a three-layer MLP with ReLU activations and 128 hidden units per layer.
It takes as input two corresponding image features and outputs a per-correspondence weight between 0 and 1 via a sigmoid activation.
Here we use intermediate feature maps from the depth network as the image features.
These weights are used in the weighted Procrustes pose solver.
